Two applications of logic programming to Coq

### 2020-11-06 papers/types2020/app.tex

In this appendix we list some definitions and pieces of code that may be helpful

\subsection{Interp}

In Fig.~\ref{fig:interp} we report the encoding of the vanilla meta-interpreter used in
the testing phase of the \lsti{dep_pbt} tactic. Differently from Fig.~\ref{fig:augmented} we appeal, via quotations, to Coq's defined connectives. An \lsti{atomic} proposition is one defined \lsti{Inductive}ly. The predicate \lsti{definition} hides the API call to the constructors of such a type.

@@

We list the rules for static and dynamic semantics of the language mentioned in section~\ref{ssec:dep_pbt} and related notions:
\begin{lstlisting}
Inductive has_type : tm -> typ -> Prop :=
   | T_Tru : has_type ttrue TBool
   | T_Fls : has_type tfalse TBool
    | T_Test : forall t1 t2 t3 T,
        has_type t1 TBool -> has_type t2 T -> has_type t3 T ->  has_type (tif  t1 t2 t3) T 
   | T_Zro : has_type tzero TNat
   | T_Scc : forall t1,
         has_type t1 TNat -> has_type (tsucc t1) TNat
   | T_Prd : forall t1,
        has_type t1 TNat -> has_type (tpred t1 ) TNat
   | T_Iszro : forall t1,
        has_type t1 TNat ->  has_type (tiszero t1) TBool.
Inductive nvalue : tm -> Prop :=
| nv_zero : nvalue tzero   | nv_succ : forall t, nvalue t -> nvalue (tsucc t).
Inductive bvalue : tm -> Prop :=
| bv_t : bvalue ttrue   | bv_f : bvalue tfalse. 
 Reserved Notation "t1 '===>' t2" (at level 40).
 Inductive step : tm -> tm -> Prop :=
   | ST_IfTrue : forall t1 t2,
       (tif ttrue t1 t2) ===> t1
   | ST_IfFalse : forall t1 t2,
       (tif tfalse t1 t2) ===> t2
   | ST_If : forall t1 t1' t2 t3,
       t1 ===> t1' -> (tif t1 t2 t3) ===> (tif t1' t2 t3)
   | ST_Succ : forall t1 t1',
       t1 ===> t1' -> (tsucc t1) ===> (tsucc t1')
   | ST_PredZero : (tpred tzero) ===> tzero
   | ST_PredSucc : forall t1,
       nvalue t1 -> (tpred (tsucc t1)) ===> t1
   | ST_Pred : forall t1 t1',
       t1 ===> t1' -> (tpred t1) ===> (tpred t1')
   | ST_IszeroZero : (tiszero tzero) ===> ttrue
   | ST_IszeroSucc : forall t1,
        nvalue t1 ->  (tiszero (tsucc t1)) ===> tfalse
   | ST_Iszero : forall t1 t1',
       t1 ===> t1' -> (tiszero t1) ===> (tiszero t1')
 where "t1 '===>' t2" := (step t1 t2).
Inductive notstuck (e : tm) (Step : tm -> tm -> Prop) : Prop :=
  | pn : nvalue e  -> notstuck e Step
  | pb : bvalue e -> notstuck e Step
  | ps e' : Step e e' -> notstuck e Step.
\end{lstlisting}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:

>>>>

In this appendix we list some definitions and pieces of code that have been mentioned in the main paper.

\subsection{The vanilla meta-interpreter}

In Fig.~\ref{fig:interp} we report the encoding of the vanilla meta-interpreter used in
the testing phase of the \lsti{dep_pbt} tactic. Differently from Fig.~\ref{fig:kernel} we appeal, via quotations, to Coq's defined connectives. An \lsti{atomic} proposition is one defined \lsti{Inductive}ly. The predicate \lsti{atomic} makes sure that \lsti{Atom} is \emph{not} a defined logical connective.

@@

We list the rules for static and dynamic semantics of the language mentioned in section~\ref{ssec:dep_pbt} and related notions:
\begin{lstlisting}
Inductive has_type : tm -> typ -> Prop :=
   | T_Tru : has_type ttrue TBool
   | T_Fls : has_type tfalse TBool
    | T_Test : forall t1 t2 t3 T,
        has_type t1 TBool -> has_type t2 T -> has_type t3 T ->  has_type (tif  t1 t2 t3) T 
   | T_Zro : has_type tzero TNat
   | T_Scc : forall t1,  has_type t1 TNat -> has_type (tsucc t1) TNat
   | T_Prd : forall t1,  has_type t1 TNat -> has_type (tpred t1 ) TNat
   | T_Iszro : forall t1,  has_type t1 TNat ->  has_type (tiszero t1) TBool.
\end{lstlisting}

\begin{lstlisting}
Inductive nvalue : tm -> Prop :=
 | nv_zero : nvalue tzero
 | nv_succ : forall t, nvalue t -> nvalue (tsucc t).
Inductive bvalue : tm -> Prop :=
 | bv_t : bvalue ttrue
 | bv_f : bvalue tfalse. 
Reserved Notation "t1 '===>' t2" (at level 40).
Inductive step : tm -> tm -> Prop :=
   | ST_IfTrue : forall t1 t2,  (tif ttrue t1 t2) ===> t1
   | ST_IfFalse : forall t1 t2, (tif tfalse t1 t2) ===> t2
   | ST_If : forall t1 t1' t2 t3,
       t1 ===> t1' -> (tif t1 t2 t3) ===> (tif t1' t2 t3)
   | ST_Succ : forall t1 t1',
       t1 ===> t1' -> (tsucc t1) ===> (tsucc t1')
   | ST_PredZero : (tpred tzero) ===> tzero
   | ST_PredSucc : forall t1,
       nvalue t1 -> (tpred (tsucc t1)) ===> t1
   | ST_Pred : forall t1 t1',
       t1 ===> t1' -> (tpred t1) ===> (tpred t1')
   | ST_IszeroZero : (tiszero tzero) ===> ttrue
   | ST_IszeroSucc : forall t1,
        nvalue t1 ->  (tiszero (tsucc t1)) ===> tfalse
   | ST_Iszero : forall t1 t1',
       t1 ===> t1' -> (tiszero t1) ===> (tiszero t1')
 where "t1 '===>' t2" := (step t1 t2).
Inductive notstuck (e : tm) (Step : tm -> tm -> Prop) : Prop :=
  | pn : nvalue e  -> notstuck e Step
  | pb : bvalue e -> notstuck e Step
  | ps e' : Step e e' -> notstuck e Step.
\end{lstlisting}
%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main"
%%% End:
